
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
% http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
%
% John Carter Haley.


\documentclass[11pt]{article}
% packages.
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}

% formatting
\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}
% commands
\newcommand{\name}[1]{\begin{center}\section*{\huge #1}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.7cm}\section*{#1}\vspace{-0.2cm}\hrule\vspace{0.2cm}}
\newcommand{\objective}[1]{\section*{#1}\vspace{-0.3cm}}


\begin{document}

\name{J. Carter Haley}
\topinfo{7 Greenhill St. $\cdot$ Charleston, SC $\cdot$  29401}
\topinfo{C: +1 (843) 822-7324 $\vert$ john.haleyb@outlook.com $\vert$ LinkedIn: jcarterhaley}

\objective{Objective}
\setlength\parindent{0cm}
My goal is to serve an industry leading institution, and support its interest while furthering my professional development. I am driven by opportunities that facilitate personal growth. There is always something to learn, let's connect! \\

\resumesection{Experience}
\textbf{Capgemini},\textbf{\textit{ Staff Consultant}}\hfill \textbf{\textit{Anticipated Start Date:}} August 2019\\
 Columbia, SC
%
\\
\\
\textbf{Blackbaud},\textbf{\textit{ Data Science Intern}}\hfill May 2018 to May 2019\\
 Daniel Island, SC
\begin{itemize}
	\item Designed a model to predict the lifetime value of donors, implemented in Python.
	\item Led a Thought Leadership project on End of Year philanthropists.
	\item Deployed models on AWS distributed computing environment.
	\item Built an ELT (Extract Load Transform) from Azure to visualize 3B+ transactions in the social good space.\\
\end{itemize}
\textbf{Smithey Ironware Company},\textbf{\textit{ Data Science} \& \textit{Analytics Intern}} \hfill March 2017 to May 2019\\
Charleston, SC
\begin{itemize}
	\item Segmented consumers based on insights derived from e-commerce transactions.
	\item Mined and analyzed Smithey's data assets.
	\item Created interactive tools to drive marketing strategy and lead consumer research.\\
\end{itemize}

\resumesection{Education}
\textbf{The College of Charleston}\hfill January 2016 to May 2019\\
 Charleston, SC
\begin{itemize}
	\item Bachelor of Science in Data Science \& Economics
	\item \textit{President’s List 2016} $\vert$ \textit{Dean’s List 2017} \& \textit{2019}.
	\item  Executive Board, President, Club Squash.
	\item ImpactX Scholar \& Member of the Interdisciplinary Center for Applied Technology.\\
\end{itemize}

\resumesection{Outreach}
\textbf{Kids on Point}, \textbf{\textit{Volunteer} \& \textit{Coach}}\hfill February 2016 to May 2018\\
 Charleston, SC
\begin{itemize}
	\item Tutored, mentored, and coached underserved youth from Charleston County schools.
	\item Networked with prospective donors both during and outside of programming.\\
\end{itemize}
\textbf{St. George's School}, \textbf{\textit{Prefect}} \hfill September 2012 to May 2014\\Newport, RI
\begin{itemize}
	\item Served as a liaison between faculty in students within Diman dormitory
	\item Facilitated a safe and comfortable atmosphere for residents.\\
\end{itemize}
\resumesection{Skills  \& Interests}
\setlength\parindent{0cm}\normalfont Python $\cdot$ Azure Databricks $\cdot$ Amazon Web Services $\cdot$ Java $\cdot$ R $\cdot$ Econometrics $\cdot$ Statistics  $\cdot$ Technical Writing $\cdot$ America's Cup Bermuda, \textit{Deckhand}, Spirit of South Carolina $\cdot$ College of Charleston Academic Excellence Award\\
\centerline{Soft Skills: Adaptability $\cdot$ Clarity $\cdot$ Collaboration $\cdot$ Enthusiasm $\cdot$ Organization}
\end{document}
